---
title: "Log. Det. Exploration"
author: "Leonardo Uchoa"
date: "3/22/2020"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Context

- The problem was that for many scenarios the algorithm failed at the very first iteration.

- Exploration of the log-likelihood for those cases showed that the issue was $log|\Sigma| = \infty$

- Further exploration showed that this was aggravated along with sample size

## Idea

- Calculate $log|\Sigma|$ for many scenarios of $\sigma^2_1,\sigma^2_2,a,\rho$ where the initial step is true value itself.

- Do this calculation with increasing sample size 2~3 times with different seeds, in case we're missing numerical problems.

- Save the output to disk for "good" practice 

## In R

>- Create a grid matrix with values for $\sigma^2_1,\sigma^2_2,a,\rho$

>- Create a vector of increasing sample sizes 

>- For any number of seeds (replication) loop over the grid and sample size vector with the `fit_biwm` code for estimation.\footnote{That implies the 3 for loops}

>- Hope your advisor doesn't call you dumb

## Results - Old Code

```{r}
arqs_new <- dir("../mle_scripts/block_matrix/autocov_test_new/autocovs_dets/",full.names = TRUE)

sum_isInf_matrix_new <- matrix(0,length(arqs_new),3)

for(i in seq_along(arqs_new)){
  
  load(arqs_new[i])
  
  sum_isInf_matrix_new[i,1] <- as.integer(
    stringr::str_extract(arqs_new[i],"\\d+"))
  
  sum_isInf_matrix_new[i,2:ncol(sum_isInf_matrix_new)] <- colSums(apply(
    do.call(cbind,det_out_list),2,is.infinite))
  
}

sum_isInf_matrix_new <- as.data.frame(sum_isInf_matrix_new)
sum_isInf_matrix_new <- sum_isInf_matrix_new[order(sum_isInf_matrix_new$V1),]

colnames(sum_isInf_matrix_new) <- c("Sample_size","1st_seed","2nd_seed")

# kableExtra::kable_styling(knitr::kable(sum_isInf_matrix_new,),
#                           font_size = 7)

arqs_old <- dir("../mle_scripts/block_matrix/autocov_test_old/autocovs_dets/",full.names = TRUE)

sum_isInf_matrix_old <- matrix(0,length(arqs_old),4)

for(i in seq_along(arqs_old)[-1]){
  
  load(arqs_old[i])
  
  sum_isInf_matrix_old[i,1] <- as.integer(
    stringr::str_extract(arqs_old[i],"\\d+"))
  
  sum_isInf_matrix_old[i,2:4] <- colSums(apply(
    log(do.call(cbind,det_out_list)),2,is.infinite))
  
}

sum_isInf_matrix_old <- as.data.frame(sum_isInf_matrix_old)
sum_isInf_matrix_old <- sum_isInf_matrix_old[order(sum_isInf_matrix_old$V1),]

pct_sum_isInf_matrix_old <- round(cbind(sum_isInf_matrix_old[,1],
      apply(sum_isInf_matrix_old[,2:4],2,function(x){x / 8000 * 100})),2)

colnames(sum_isInf_matrix_old) <- c("Sample_size","1st_seed","2nd_seed","3rd_seed")

kableExtra::kable_styling(
  knitr::kable(pct_sum_isInf_matrix_old[2:16,],
               caption = "Experimentation with Old Code. Pct out of 8000 grid values",row.names = FALSE),
  font_size = 7)

```

## Results - Old Code

```{r}
kableExtra::kable_styling(
  knitr::kable(pct_sum_isInf_matrix_old[16:32,],
               caption = "Experimentation with Old Code. Pct out of 8000 grid values",row.names = FALSE),
  font_size = 7)
```

## Results - Code With Block Matrix Implementations

```{r}
kableExtra::kable_styling(
  knitr::kable(sum_isInf_matrix_new,
               caption = "Experimentation with New Code. Pct out of 8000 grid values",row.names = FALSE),
  font_size = 7)
```

